---
title: "Diplomacy Plots"
author: "Yana Otlan"
date: "5/1/2020"
output:
  html_document:
  toc: true
self_contained: true
github_document:
  toc: true
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
                    encoding=encoding,
                    output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Diplomatic Sentiment Plots

## USA

Plot using all the data, inlcuding the UNSC records. Red and blue shaded areas are US-USSR MIDs that occurred between 1955 and 1964. All plots made with "Threatening" + "Angry" sentiment measure (higher score = more hawkish)




```{r, echo = F, message = F, warning = F, fig.fullwidth = T}

library(tidyverse)
library(plotly)

us_full = read_csv("us_full.csv")
mids_table = read_csv("mids_table.csv")

us_plot = ggplot() +
  geom_smooth(data=us_full, aes(x = date, y = avg_threat, color = public), span = 0.10, se = F) +
  #geom_line(data=us_full, aes(x = date, y = avg_threat, color = public)) +
  geom_hline(yintercept = 0, color = "black", size = 0.3) +
  scale_fill_manual(values=c("USA" = "blue", "USSR" = "red")) +
  geom_rect(data = mids_table, 
            aes(NULL,NULL,xmin = stdate, xmax = enddate, ymin = 0, ymax = 0.07,
                fill = initiator,
                text = paste("Outcome: ", outcome, 
                             "<br>Hostility by Initiator: ", source_host,
                             "<br>Hostility by Target:", target_host)), 
            colour=NA,  alpha = 0.1) + 
  labs(title = "Weekly Sentiment of Diplomatic Statements \nby the United States (with UNSC)",
     subtitle = "Measure:Threatening + Angry (higher score = more hawkish)",
     x = "Year-Month", 
     y = "Hawkish Rhetoric", 
     color = " ") +
  scale_color_manual(labels = c("Private", "Public"), 
                     values = c("lightblue", "darkblue")) +
  scale_fill_manual(' ',
                      values = c("blue", "red")) +
  scale_x_date(date_labels = "%Y", 
               date_breaks = "1 year") +
  #scale_x_datetime(breaks=unique(year(date)),
               #labels = date_format("%Y")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        axis.text.y = element_text(size  = 12),
        axis.title=element_text(size=14,face="bold"),
        panel.background = element_rect(fill = "white",
                                        colour = "white",
                                        size = 0.25, linetype = "solid"),
        panel.grid.major = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"),
        axis.line = element_line(colour = "black"))

ggplotly(us_plot)

```

Plot without UNSC records. Only made for the U.S. because I don't have records of Soviet statements yet. 




```{r, echo = F, message = F, warning = F}
us_noun = read_csv("us_noun.csv")

usa_noun_plot = ggplot() +
  geom_smooth(data=us_noun, aes(x = date, y = avg_threat, color = public), span = 0.10, se = F) +
  #geom_line(data=us_full, aes(x = date, y = avg_threat, color = public)) +
  geom_hline(yintercept = 0, color = "black", size = 0.3) +
  scale_fill_manual(values=c("USA" = "blue", "USSR" = "red")) +
  geom_rect(data = mids_table, 
            aes(NULL,NULL,xmin = stdate, xmax = enddate, ymin = 0, ymax = 0.07,
                fill = initiator,
                text = paste("Outcome: ", outcome, 
                             "<br>Hostility by Initiator: ", source_host,
                             "<br>Hostility by Target:", target_host)), 
            colour=NA,  alpha = 0.1) + 
  labs(title = "Weekly Sentiment of Diplomatic Statements \nby the United States (no UNSC)",
     subtitle = "Measure:Threatening + Angry (higher score = more hawkish)",
     x = "Year-Month", 
     y = "Hawkish Rhetoric", 
     color = " ") +
  scale_color_manual(labels = c("Private", "Public"), 
                     values = c("lightblue", "darkblue")) +
  scale_fill_manual(' ',
                      values = c("blue", "red")) +
  scale_x_date(date_labels = "%Y", 
               date_breaks = "1 year") +
  #scale_x_datetime(breaks=unique(year(date)),
               #labels = date_format("%Y")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        axis.text.y = element_text(size  = 12),
        axis.title=element_text(size=14,face="bold"),
        panel.background = element_rect(fill = "white",
                                        colour = "white",
                                        size = 0.25, linetype = "solid"),
        panel.grid.major = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"),
        axis.line = element_line(colour = "black"))


ggplotly(usa_noun_plot)

```


## USSR 

Plots for the Soviet Union



```{r, echo = F, message = F, warning = F}
ussr_full = read_csv("ussr_full.csv")

ussr_plot = ggplot() +
  geom_smooth(data=ussr_full, aes(x = date, y = avg_threat, color = public), span = 0.1, se=F) +
  #geom_line(data=us_full, aes(x = date, y = avg_threat, color = public)) +
  geom_hline(yintercept = 0, color = "black", size = 0.3) +
  #scale_fill_manual(values=c("USA" = "blue", "USSR" = "red")) +
  geom_rect(data = mids_table, 
            aes(NULL,NULL,xmin = stdate, xmax = enddate, ymin = 0, ymax = 0.1,
                fill = initiator,
                text = paste("Outcome: ", outcome, 
                             "<br>Hostility by Initiator: ", source_host,
                             "<br>Hostility by Target:", target_host)), 
            colour=NA,  alpha = 0.1) + 
  labs(title = "Weekly Sentiment of Diplomatic Statements \nby the USSR (with UNSC)",
     subtitle = "Measure:Threatening + Angry (higher score = more hawkish)",
     x = "Year-Month", 
     y = "Hawkish Rhetoric", 
     color = " ") +
  scale_color_manual(labels = c("Private", "Public"), 
                     values = c("lightblue", "darkblue")) +
  scale_fill_manual(' ',
                      values = c("blue", "red")) +
  scale_x_date(date_labels = "%Y", 
               date_breaks = "1 year") +
  #scale_x_datetime(breaks=unique(year(date)),
               #labels = date_format("%Y")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        axis.text.y = element_text(size  = 12),
        axis.title=element_text(size=14,face="bold"),
        panel.background = element_rect(fill = "white",
                                        colour = "white",
                                        size = 0.25, linetype = "solid"),
        panel.grid.major = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                        colour = "lightgrey"),
        axis.line = element_line(colour = "black"))



ggplotly(ussr_plot)
```
